---
title: "remap_background_conservation"
author: "juphilip"
date: "6/17/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# What's happening?
need background for conservation plots
get similar number of AS events for each comparison
generate lists with event ids (potentially multiple for each)
then get phyloP and phastCons scores (with andrew's script in commandline)
then plot them in remap_conservation_plots.Rmd

open remap_conservation_plots.Rmd script too for labels and all_phastcons and all_phyloP data

```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotrix)
library(stringr)
library(cowplot)

theme_set(theme_cowplot())
```

```{r load AS event lists}
human_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_human.txt", header = FALSE, stringsAsFactors = FALSE)

chimp_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_chimp.txt", header = FALSE, stringsAsFactors = FALSE)

orang_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_orang.txt", header = FALSE, stringsAsFactors = FALSE)
```

```{r load psi values to filter as-events a little more}
load("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_as_nmd_events.RData")

event_psi_filtered <- all_events_psi_restricted %>% 
  group_by(event_id) %>% 
  mutate(sum = sum(avg_psi)) %>% 
  filter(sum > 0) %>% 
  filter(sum < 10)
```

```{r find common AS for each comparison}
human_chimp_AS <- human_AS[which(human_AS$V1 %in% chimp_AS$V1),]
human_chimp_AS_SE <- human_chimp_AS[which(str_detect(human_chimp_AS, "SE"))]
human_chimp_AS_AF <- human_chimp_AS[which(str_detect(human_chimp_AS, "AF"))]

# exclude events that are zero or 10
human_chimp_AS_SE_strict <- human_chimp_AS_SE[which(human_chimp_AS_SE %in% event_psi_filtered$event_id)]
human_chimp_AS_AF_strict <- human_chimp_AS_AF[which(human_chimp_AS_AF %in% event_psi_filtered$event_id)]

human_orang_AS <- human_AS[which(human_AS$V1 %in% orang_AS$V1),]
human_orang_AS_SE <- human_orang_AS[which(str_detect(human_orang_AS, "SE"))]
human_orang_AS_AF <- human_orang_AS[which(str_detect(human_orang_AS, "AF"))]

# exclude events that are zero or 10
human_orang_AS_SE_strict <- human_orang_AS_SE[which(human_orang_AS_SE %in% event_psi_filtered$event_id)]
human_orang_AS_AF_strict <- human_orang_AS_AF[which(human_orang_AS_AF %in% event_psi_filtered$event_id)]

chimp_orang_AS <- chimp_AS[which(chimp_AS$V1 %in% orang_AS$V1),]
chimp_orang_AS_SE <- chimp_orang_AS[which(str_detect(chimp_orang_AS, "SE"))]
chimp_orang_AS_AF <- chimp_orang_AS[which(str_detect(chimp_orang_AS, "AF"))]

all_three_AS <- intersect(intersect(human_AS$V1, chimp_AS$V1), orang_AS$V1)
all_three_AS_SE <- all_three_AS[which(str_detect(all_three_AS, "SE"))]
all_three_AS_AF <- all_three_AS[which(str_detect(all_three_AS, "AF"))]

all_three_AS_SE_strict <- all_three_AS_SE[which(all_three_AS_SE %in% event_psi_filtered$event_id)]
all_three_AS_AF_strict <- all_three_AS_AF[which(all_three_AS_AF %in% event_psi_filtered$event_id)]

# at this point these event lists can be used in the other script
#save(human_orang_AS_AF_strict, human_orang_AS_SE_strict, human_chimp_AS_AF_strict, human_chimp_AS_SE_strict, all_three_AS_AF_strict, all_three_AS_SE_strict, file = "~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/background_AS_event_lists_strict.RData")
```


# all three 30
for comparison to AS-TC only events
## phastcons
randomly subsetting these lists multiple times and summarizing the results into one plot

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE_strict[sample(1:length(all_three_AS_SE_strict), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}

bg_all_three_SE_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_30_strict$SS <- revalue(bg_all_three_SE_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_all_three_SE_30_strict <-  bg_all_three_SE_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_all_three_SE_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


```{r 30 iterations for all three AF STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 30, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 30}

bg_all_three_AF_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_30_strict$SS <- revalue(bg_all_three_AF_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_30_strict <- bg_all_three_AF_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
```




# save data
```{r save data}
save.image("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/remap_background_cons.RData")

```
