---
title: "Remap_conservation_plots"
author: "juphilip"
date: "4/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
rm(list=ls(all=TRUE))
library(ggplot2)
library(cowplot)

theme_set(theme_cowplot())

get_files <- function(x){
  tryCatch(read.delim(x, header = FALSE, stringsAsFactors = FALSE, sep = "\t"), error=function(e) NULL)}

```

```{r read in conservation score files}
all_phastcons <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_splice_site_regions_phastcons.tsv", header = FALSE, stringsAsFactors = FALSE) %>% 
  separate(V4, into = c("event_type", "SS", "event_id"), sep = ";")

all_phylop <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_splice_site_regions_phylop.tsv", header = FALSE, stringsAsFactors = FALSE) %>% 
  separate(V4, into = c("event_type", "SS","event_id"), sep = ";")

```

```{r read in event lists}
all_species_distance <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/pipeline_output/human_chimp_orang/all_distances.tsv", header = TRUE, stringsAsFactors = FALSE) %>% 
  filter(constant_vars == "fraction")

astc_at_least_one <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_in_at_least_one_species.txt", header = FALSE, stringsAsFactors = FALSE)

astc_in_all <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_in_all.txt", header = FALSE, stringsAsFactors = FALSE)

## human chimp
astc_at_least_one_hc <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_at_least_one_hc.txt", header = FALSE, stringsAsFactors = FALSE)

astc_in_all_hc <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_both_hc.txt", header = FALSE, stringsAsFactors = FALSE)

## human orang
astc_at_least_one_ho <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_at_least_one_ho.txt", header = FALSE, stringsAsFactors = FALSE)

astc_in_all_ho <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_both_ho.txt", header = FALSE, stringsAsFactors = FALSE)

## chimp orang
astc_at_least_one_co <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_at_least_one_co.txt", header = FALSE, stringsAsFactors = FALSE)

astc_in_all_co <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_both_co.txt", header = FALSE, stringsAsFactors = FALSE)
```

```{r load background data}
# compiled in script "remap_background_conservation.Rmd"
load("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/remap_background_cons.RData")
```

# Three species
## ASTC at least one
### skipped exons
```{r make SE top and bottom}
astc_at_least_one_SE <- astc_at_least_one %>% 
  filter(str_detect(V1, "SE"))

astc_at_least_one_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get SE scores}
astc_at_least_one_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_SE_top$event_id | event_id %in% astc_at_least_one_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_SE_phastcons)[10:309] <- c(1:300)

astc_at_least_one_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_SE_top$event_id | event_id %in% astc_at_least_one_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phastcons_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_100, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey80") +
  geom_line(data = bg_all_three_SE_100, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),method = "gam", formula = y~s(x)) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE)) +
  scale_color_manual(values = c("blue","gold","black"), 
                     name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) 
dev.off()

# phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phastcons_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_100_strict, aes(x=position_new, ymin = m-s, ymax= m+s), fill = "grey80") +
  geom_line(data = bg_all_three_SE_100_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),method = "gam", formula = y~s(x)) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x") +
  scale_color_manual(values = c("blue","gold","black"), 
                     name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) 
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
  
# phylop with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phylop_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_100, aes(x=x,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_all_three_SE_phylop_100, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phylop_w_bg_strict_stderr.png", height = 4, width = 12, units = "in", res = 300)
test <- astc_at_least_one_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_100_strict, aes(x=x,ymin = m-e, ymax= m+e), fill = "grey75") +
  geom_line(data = bg_all_three_SE_phylop_100_strict, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

#adjusted range background stddev
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phylop_w_bg_strict_stderr.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_100_strict, aes(x=x,ymin = m-e, ymax= m+e), fill = "grey75") +
  geom_line(data = bg_all_three_SE_phylop_100_strict, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  geom_blank(data=blank, aes(x=x, y=y)) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

#adjusted range background stderr
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_SE_phylop_w_bg_strict_stderr.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_100_strict, aes(x=x,ymin = m-e, ymax= m+e), fill = "grey75") +
  geom_line(data = bg_all_three_SE_phylop_100_strict, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  geom_blank(data=blank, aes(x=x, y=y)) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()
```

### alternative first exons
```{r make AF top and bottom}
astc_at_least_one_AF <- astc_at_least_one %>% 
  filter(str_detect(V1, "AF"))

astc_at_least_one_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get AF scores}
astc_at_least_one_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_AF_top$event_id | event_id %in% astc_at_least_one_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_AF_phastcons)[10:309] <- c(1:300)

astc_at_least_one_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_AF_top$event_id | event_id %in% astc_at_least_one_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_speices/astc_at_least_one_top100_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()

# phastcons with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_AF_phastcons_w_bg.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>%
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_100, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_all_three_AF_100, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
dev.off()

# phast cons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>%
  mutate(position_new = case_when(SS == 0 ~ position-50,
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_100_strict, aes(x=position_new, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_all_three_AF_100_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
# phyloP with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_AF_phylop_w_bg.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_phylop_100, aes(x=x,ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(data = bg_all_three_AF_phylop_100, aes(x=x,y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type), method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_at_least_one_top100_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ position-50,
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_phylop_100_strict, aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(data = bg_all_three_AF_phylop_100_strict, aes(x=position_new,y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new 
                  , y=score, group = type, color = type), method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
```



## ASTC in all
### skipped exons
```{r make SE top and bottom}
astc_in_all_SE <- astc_in_all %>% 
  filter(str_detect(V1, "SE")) %>% 
  unique()

astc_in_all_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get SE scores}
astc_in_all_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_SE_top$event_id | event_id %in% astc_in_all_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_SE_phastcons)[10:309] <- c(1:300)

astc_in_all_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_SE_top$event_id | event_id %in% astc_in_all_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phastcons_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_30, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_all_three_SE_30, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons with background strict
#png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phastcons_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
pdf("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phastcons_w_bg_strict_se.pdf", height = 4, width = 12)
astc_in_all_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                 SS == 1 ~ position-250,
                                 SS == 2 ~ position-50,
                                 SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_30_strict, aes(x=position_new, ymin = m-se, ymax= m+se), fill = "grey75") +
  geom_line(data = bg_all_three_SE_30_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  geom_vline(aes(xintercept = 0), color = "grey") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
  
# phyloP with background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phylop_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_30, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey85") +
  geom_line(data = bg_all_three_SE_phylop_30, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_SE_phylop_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_SE_phylop_30_strict, aes(x=position_new, ymin = m-s, ymax= m+s), fill = "grey85") +
  geom_line(data = bg_all_three_SE_phylop_30_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()
```

### alternative first exons
```{r make AF top and bottom}
astc_in_all_AF <- astc_in_all %>% 
  filter(str_detect(V1, "AF")) %>% 
  unique()

astc_in_all_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  dplyr::select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get AF scores}
astc_in_all_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_AF_top$event_id | event_id %in% astc_in_all_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_AF_phastcons)[10:309] <- c(1:300)

astc_in_all_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_AF_top$event_id | event_id %in% astc_in_all_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  
#png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
pdf("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_AF_phastcons_w_bg_strict_se.pdf", height = 4, width = 8)
astc_in_all_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ position-50,
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  group_by(event_id, type, SS) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_30_strict, aes(x=position_new, ymin = m-se, ymax= m+se), fill = "grey85") +
  geom_line(data = bg_all_three_AF_30_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) + 
  geom_vline(xintercept=0, color="grey")
dev.off()

# phylop
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()

# phylop
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/three_species/astc_in_all_top30_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_all_three_AF_phylop_30_strict, aes(x=position_new, ymin = m-s, ymax= m+s), fill = "grey85") +
  geom_line(data = bg_all_three_AF_phylop_30_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type), method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
```


# Two species

## human chimp
### ASTC at least one
#### skipped exons
```{r make SE top and bottom}
astc_at_least_one_hc_SE <- astc_at_least_one_hc %>% 
  filter(str_detect(V1, "SE")) %>% 
  unique()

astc_at_least_one_hc_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_hc_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_hc_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_hc_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get SE scores}
astc_at_least_one_hc_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_hc_SE_top$event_id | event_id %in% astc_at_least_one_hc_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_hc_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_hc_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_hc_SE_phastcons)[10:309] <- c(1:300)

astc_at_least_one_hc_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_hc_SE_top$event_id | event_id %in% astc_at_least_one_hc_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_hc_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_hc_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_hc_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons with bg
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phastcons_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_100, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_100, aes(x=x, y=m), color = "black", size=.8) + 
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phastcons_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_100, aes(x=x, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_100, aes(x=x, y=m), color = "black", size=.8) + 
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

# phastcons with bg strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phastcons_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_100_strict, aes(x=position_new, ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_100_strict, aes(x=position_new, y=m), color = "black", size=.8) + 
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
 
# phylo with bg 
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phylop_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_phylop_100, 
              aes(x=x,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_phylop_100, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phylo with bg 
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phylop_w_bg.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_phylop_100, 
              aes(x=x,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_phylop_100, aes(x=x, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phylo with bg 
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_SE_phylop_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_phylop_100_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_phylop_100_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold","black"), name="",
                     labels = c("conserved","species-specific","ctrl"), 
                     limits = c("conserved","species-specific","ctrl")) +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
```

#### alternative first exons
```{r make AF top and bottom}
astc_at_least_one_hc_AF <- astc_at_least_one_hc %>% 
  filter(str_detect(V1, "AF"))

astc_at_least_one_hc_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_hc_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_hc_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_hc_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get AF scores}
astc_at_least_one_hc_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_hc_AF_top$event_id | event_id %in% astc_at_least_one_hc_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_hc_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_hc_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_hc_AF_phastcons)[10:309] <- c(1:300)

astc_at_least_one_hc_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_hc_AF_top$event_id | event_id %in% astc_at_least_one_hc_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_hc_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_hc_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_hc_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_hc_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()

# phast cons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_hc_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_AF_100_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_AF_100_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type), method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  
# phyloP
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_hc_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()

# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_at_least_one_top100_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_hc_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_AF_phylop_100_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_AF_phylop_100_strict, aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
```


### ASTC in both
#### skipped exons
```{r make SE top and bottom}
astc_in_all_hc_SE <- astc_in_all_hc %>% 
  filter(str_detect(V1, "SE"))

astc_in_all_hc_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_hc_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_hc_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_hc_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get SE scores}
astc_in_all_hc_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_hc_SE_top$event_id | event_id %in% astc_in_all_hc_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_hc_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_hc_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_hc_SE_phastcons)[10:309] <- c(1:300)

astc_in_all_hc_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_hc_SE_top$event_id | event_id %in% astc_in_all_hc_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_hc_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_hc_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_hc_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons with bg strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_SE_phastcons_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_hc_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
   mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_SE_phylop_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_hc_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
   mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_SE_phylop_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_SE_phylop_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()
  
```

#### alternative first exons
```{r make AF top and bottom}
astc_in_all_hc_AF <- astc_in_all_hc %>% 
  filter(str_detect(V1, "AF")) %>% 
  unique()

astc_in_all_hc_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_hc_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_hc_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_hc_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get AF scores}
astc_in_all_hc_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_hc_AF_top$event_id | event_id %in% astc_in_all_hc_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_hc_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_hc_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_hc_AF_phastcons)[10:309] <- c(1:300)

astc_in_all_hc_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_hc_AF_top$event_id | event_id %in% astc_in_all_hc_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_hc_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_hc_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_hc_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_hc_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  
# phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_hc_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_AF_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_AF_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_hc_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
# phylop with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_chimp/astc_in_all_top30_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_hc_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_chimp_AF_phylop_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_chimp_AF_phylop_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
```




## human orang
### ASTC at least one
#### skipped exons
```{r make SE top and bottom}
astc_at_least_one_ho_SE <- astc_at_least_one_ho %>% 
  filter(str_detect(V1, "SE")) %>% 
  unique()

astc_at_least_one_ho_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_ho_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_at_least_one_ho_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_ho_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get SE scores}
astc_at_least_one_ho_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_ho_SE_top$event_id | event_id %in% astc_at_least_one_ho_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_ho_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_ho_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_ho_SE_phastcons)[10:309] <- c(1:300)

astc_at_least_one_ho_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_ho_SE_top$event_id | event_id %in% astc_at_least_one_ho_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_ho_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_ho_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_ho_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_ho_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_SE_phastcons_w_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_ho_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_SE_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_SE_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

# phylop
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_ho_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phylop with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_SE_phylop_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_ho_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_SE_phylop_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_SE_phylop_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
  
```

#### alternative first exons
```{r make AF top and bottom}
astc_at_least_one_ho_AF <- astc_at_least_one_ho %>% 
  filter(str_detect(V1, "AF"))

astc_at_least_one_ho_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_ho_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_ho_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_ho_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get AF scores}
astc_at_least_one_ho_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_ho_AF_top$event_id | event_id %in% astc_at_least_one_ho_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_ho_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_ho_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_ho_AF_phastcons)[10:309] <- c(1:300)

astc_at_least_one_ho_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_ho_AF_top$event_id | event_id %in% astc_at_least_one_ho_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_ho_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_ho_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_ho_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

# phastcons
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_ho_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  
# phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top100_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_ho_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_AF_100_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_AF_100_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()

# phylop
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top30_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_ho_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()

# phylop with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_at_least_one_top100_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_ho_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ position-50,
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_AF_phylop_100_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_AF_phylop_100_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
```


### ASTC in both
#### skipped exons
```{r make SE top and bottom}
astc_in_all_ho_SE <- astc_in_all_ho %>% 
  filter(str_detect(V1, "SE")) %>% 
  unique()

astc_in_all_ho_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_ho_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_ho_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_ho_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get SE scores}
astc_in_all_ho_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_ho_SE_top$event_id | event_id %in% astc_in_all_ho_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_ho_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_ho_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_ho_SE_phastcons)[10:309] <- c(1:300)

astc_in_all_ho_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_ho_SE_top$event_id | event_id %in% astc_in_all_ho_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_ho_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_ho_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_ho_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_ho_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

#phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_SE_phastcons_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_ho_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_SE_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_SE_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()

# phyloP
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_ho_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

# phyloP with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_SE_phylop_w_bg_strict.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_ho_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-250,
                                  SS == 2 ~ position-50,
                                  SS == 3 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_SE_phylop_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_SE_phylop_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE), scales = "free_x")
dev.off()
  
```

#### alternative first exons
```{r make AF top and bottom}
astc_in_all_ho_AF <- astc_in_all_ho %>% 
  filter(str_detect(V1, "AF")) %>% 
  unique()

astc_in_all_ho_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_ho_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_ho_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_ho_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get AF scores}
astc_in_all_ho_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_ho_AF_top$event_id | event_id %in% astc_in_all_ho_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_ho_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_ho_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_ho_AF_phastcons)[10:309] <- c(1:300)

astc_in_all_ho_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_ho_AF_top$event_id | event_id %in% astc_in_all_ho_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_ho_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_ho_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_ho_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_ho_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  
# phastcons with background strict
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_AF_phastcons_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_ho_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_AF_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_AF_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()

#phyloP
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_ho_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
# phyloP with strict background
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/human_orang/astc_in_all_top30_AF_phylop_w_bg_strict.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_ho_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  mutate(position_new = case_when(SS == 0 ~ (position-50),
                                  SS == 1 ~ position-50,
                                  SS == 2 ~ position-250)) %>% 
  ggplot() +
  geom_ribbon(data = bg_human_orang_AF_phylop_30_strict, 
              aes(x=position_new,ymin = m-s, ymax= m+s), fill = "grey75") +
  geom_line(data = bg_human_orang_AF_phylop_30_strict, 
              aes(x=position_new, y=m), color = "black", size=.8) +
  geom_smooth(aes(x=position_new, y=score, group = type, color = type),
              method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
```




## chimp orang
### ASTC at least one
#### skipped exons
```{r make SE top and bottom}
astc_at_least_one_co_SE <- astc_at_least_one_co %>% 
  filter(str_detect(V1, "SE")) %>% 
  unique()

astc_at_least_one_co_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_co_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_co_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_co_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get SE scores}
astc_at_least_one_co_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_co_SE_top$event_id | event_id %in% astc_at_least_one_co_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_co_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_co_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_co_SE_phastcons)[10:309] <- c(1:300)

astc_at_least_one_co_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_co_SE_top$event_id | event_id %in% astc_at_least_one_co_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_co_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_co_SE_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_co_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_at_least_one_top100_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_co_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_at_least_one_top100_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_at_least_one_co_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
  
```

#### alternative first exons
```{r make AF top and bottom}
astc_at_least_one_co_AF <- astc_at_least_one_co %>% 
  filter(str_detect(V1, "AF"))

astc_at_least_one_co_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_co_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=100)

astc_at_least_one_co_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_at_least_one_co_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=100)
  
```

```{r get AF scores}
astc_at_least_one_co_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_at_least_one_co_AF_top$event_id | event_id %in% astc_at_least_one_co_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_co_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_co_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_co_AF_phastcons)[10:309] <- c(1:300)

astc_at_least_one_co_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_at_least_one_co_AF_top$event_id | event_id %in% astc_at_least_one_co_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_at_least_one_co_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_at_least_one_co_AF_bottom$event_id ~ "conserved"))

colnames(astc_at_least_one_co_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_at_least_one_top100_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_co_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_at_least_one_top100_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_at_least_one_co_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
```


### ASTC in both
#### skipped exons
```{r make SE top and bottom}
astc_in_all_co_SE <- astc_in_all_co %>% 
  filter(str_detect(V1, "SE"))

astc_in_all_co_SE_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_co_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_co_SE_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_co_SE$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get SE scores}
astc_in_all_co_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_co_SE_top$event_id | event_id %in% astc_in_all_co_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_co_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_co_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_co_SE_phastcons)[10:309] <- c(1:300)

astc_in_all_co_SE_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_co_SE_top$event_id | event_id %in% astc_in_all_co_SE_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_co_SE_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_co_SE_bottom$event_id ~ "conserved"))

colnames(astc_in_all_co_SE_phylop)[10:309] <- c(1:300)

```

```{r make SE plot}
labels_SE <-  c("0" = "Upstream 5'SS", "1" = "3'SS", "2" = "5'SS", "3" = "Downstream 3'SS")
# make dataset long first
png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_in_all_top30_SE_phastcons.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_co_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_in_all_top30_SE_phylop.png", height = 4, width = 12, units = "in", res = 300)
astc_in_all_co_SE_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), labeller = labeller(SS = labels_SE))
dev.off()
  
```

#### alternative first exons
```{r make AF top and bottom}
astc_in_all_co_AF <- astc_in_all_co %>% 
  filter(str_detect(V1, "AF")) %>% 
  unique()

astc_in_all_co_AF_top <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_co_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  head(n=30)

astc_in_all_co_AF_bottom <- all_species_distance %>% 
  filter(event_id %in% astc_in_all_co_AF$V1) %>% 
  group_by(event_id) %>% 
  mutate(sum_inner_dist=sum(inner_dist)) %>% 
  select(event_id, sum_inner_dist) %>% 
  unique() %>% 
  na.omit() %>% 
  arrange(desc(sum_inner_dist)) %>% 
  tail(n=30)
  
```

```{r get AF scores}
astc_in_all_co_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% astc_in_all_co_AF_top$event_id | event_id %in% astc_in_all_co_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_co_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_co_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_co_AF_phastcons)[10:309] <- c(1:300)

astc_in_all_co_AF_phylop <- all_phylop %>% 
  filter(event_id %in% astc_in_all_co_AF_top$event_id | event_id %in% astc_in_all_co_AF_bottom$event_id) %>% 
  mutate(type = case_when(event_id %in% astc_in_all_co_AF_top$event_id ~ "species-specific",
                          event_id %in% astc_in_all_co_AF_bottom$event_id ~ "conserved"))

colnames(astc_in_all_co_AF_phylop)[10:309] <- c(1:300)

```

```{r make AF plot}
# AF labeller
labels_AF <- c("0" = "Upstream 5'SS", "1" = "Downstream 5'SS", "2" = "3'SS")

# make dataset long first

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_in_all_top30_AF_phastcons.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_co_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")
dev.off()
  

png("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/chimp_orang/astc_in_all_top30_AF_phylop.png", height = 4, width = 8, units = "in", res = 300)
astc_in_all_co_AF_phylop %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("blue","gold"), name="") +
  labs(x="Position", y="Conservation (PhyloP)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF))
dev.off()
  
```


```{r save event list data}
save.image("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/top_bottom_event_lists_updated.RData")
```

