---
title: "remap_background_conservation"
author: "juphilip"
date: "6/17/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

# What's happening?
need background for conservation plots
get similar number of AS events for each comparison
generate lists with event ids (potentially multiple for each)
then get phyloP and phastCons scores (with andrew's script in commandline)
then plot them in remap_conservation_plots.Rmd

open remap_conservation_plots.Rmd script too for labels and all_phastcons and all_phyloP data

```{r setup, include=FALSE}
rm(list = ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(plotrix)
library(stringr)
library(cowplot)

theme_set(theme_cowplot())
```

```{r load AS event lists}
human_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_human.txt", header = FALSE, stringsAsFactors = FALSE)

chimp_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_chimp.txt", header = FALSE, stringsAsFactors = FALSE)

orang_AS <- read.delim("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/as_events/as_events_orang.txt", header = FALSE, stringsAsFactors = FALSE)
```

```{r load psi values to filter as-events a little more}
load("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/astc_events/astc_as_nmd_events.RData")

event_psi_filtered <- all_events_psi_restricted %>% 
  group_by(event_id) %>% 
  mutate(sum = sum(avg_psi)) %>% 
  filter(sum > 0) %>% 
  filter(sum < 10)
```

```{r find common AS for each comparison}
human_chimp_AS <- human_AS[which(human_AS$V1 %in% chimp_AS$V1),]
human_chimp_AS_SE <- human_chimp_AS[which(str_detect(human_chimp_AS, "SE"))]
human_chimp_AS_AF <- human_chimp_AS[which(str_detect(human_chimp_AS, "AF"))]

# exclude events that are zero or 10
human_chimp_AS_SE_strict <- human_chimp_AS_SE[which(human_chimp_AS_SE %in% event_psi_filtered$event_id)]
human_chimp_AS_AF_strict <- human_chimp_AS_AF[which(human_chimp_AS_AF %in% event_psi_filtered$event_id)]

human_orang_AS <- human_AS[which(human_AS$V1 %in% orang_AS$V1),]
human_orang_AS_SE <- human_orang_AS[which(str_detect(human_orang_AS, "SE"))]
human_orang_AS_AF <- human_orang_AS[which(str_detect(human_orang_AS, "AF"))]

# exclude events that are zero or 10
human_orang_AS_SE_strict <- human_orang_AS_SE[which(human_orang_AS_SE %in% event_psi_filtered$event_id)]
human_orang_AS_AF_strict <- human_orang_AS_AF[which(human_orang_AS_AF %in% event_psi_filtered$event_id)]

chimp_orang_AS <- chimp_AS[which(chimp_AS$V1 %in% orang_AS$V1),]
chimp_orang_AS_SE <- chimp_orang_AS[which(str_detect(chimp_orang_AS, "SE"))]
chimp_orang_AS_AF <- chimp_orang_AS[which(str_detect(chimp_orang_AS, "AF"))]

all_three_AS <- intersect(intersect(human_AS$V1, chimp_AS$V1), orang_AS$V1)
all_three_AS_SE <- all_three_AS[which(str_detect(all_three_AS, "SE"))]
all_three_AS_AF <- all_three_AS[which(str_detect(all_three_AS, "AF"))]

all_three_AS_SE_strict <- all_three_AS_SE[which(all_three_AS_SE %in% event_psi_filtered$event_id)]
all_three_AS_AF_strict <- all_three_AS_AF[which(all_three_AS_AF %in% event_psi_filtered$event_id)]

# at this point these event lists can be used in the other script
#save(human_orang_AS_AF_strict, human_orang_AS_SE_strict, human_chimp_AS_AF_strict, human_chimp_AS_SE_strict, all_three_AS_AF_strict, all_three_AS_SE_strict, file = "~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/background_AS_event_lists_strict.RData")
```

# all three 100
for comparison to AS-TC only events
## phastcons
try out randomly subsetting these lists multiple times and summarizing the results into one plot

```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE[sample(1:length(all_three_AS_SE), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_all_three_SE_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_30$SS <- revalue(bg_all_three_SE_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_SE_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS))
  
```

```{r 100 iterations for all three SE STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE_strict[sample(1:length(all_three_AS_SE_strict), 100, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations STRICT }
# maybe

bg_all_three_SE_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)


library(plyr)
bg_all_three_SE_100_strict$SS <- revalue(bg_all_three_SE_100_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_all_three_SE_100_strict <- bg_all_three_SE_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_all_three_SE_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 100 iterations for all three AF}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF[sample(1:length(all_three_AS_AF), 100, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 100}
bg_all_three_AF_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_100$SS <- revalue(bg_all_three_AF_100$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_AF_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))

```

```{r 100 iterations for all three AF STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 100, replace=TRUE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 100 strict}
bg_all_three_AF_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_100_strict$SS <- revalue(bg_all_three_AF_100_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_100_strict <- bg_all_three_AF_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL), scales = "free_x")

ggplot(bg_all_three_AF_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-e, ymax= m+e), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL), scales = "free_x")
```

```{r 100 iterations for all three AF STRICT 30 events}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 30, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  #plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
  plot_list[[i]] <- plot1
}

```

```{r}
pdf("~/Desktop/phastcons_bg_AF_test.pdf", height = 5, width = 7)
for (i in 1:length(all_three_AS_AF_strict)){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[i]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) +
  ggtitle(all_three_AS_AF_strict[i])

  #plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
  print(plot1)
}
dev.off()
```

```{r collapse all three AF 30 strict}
bg_all_three_AF_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_30_strict$SS <- revalue(bg_all_three_AF_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_30_strict <- bg_all_three_AF_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL), scales = "free_x")

ggplot(bg_all_three_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-e, ymax= m+e), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL), scales = "free_x")
```

## phyloP
```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE[sample(1:length(all_three_AS_SE), 100, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_all_three_SE_phylop_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_phylop_30$SS <- revalue(bg_all_three_SE_phylop_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_SE_phylop_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for all three SE STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE_strict[sample(1:length(all_three_AS_SE_strict), 100, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_all_three_SE_phylop_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

bg_all_three_SE_phylop_100_strict <- bg_all_three_SE_phylop_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 
library(plyr)
bg_all_three_SE_phylop_100_strict$SS <- revalue(bg_all_three_SE_phylop_100_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_SE_phylop_100_strict, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-e, ymax= m+e), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))

ggplot(bg_all_three_SE_phylop_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL), scales = "free_x")
  
```

```{r 100 iterations for all three AF}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF[sample(1:length(all_three_AS_AF), 100, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 100}
bg_all_three_AF_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_phylop_100$SS <- revalue(bg_all_three_AF_phylop_100$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_AF_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
```

```{r 100 iterations for all three AF STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 100, replace=TRUE)]

test_all_three_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 100}
bg_all_three_AF_phylop_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_phylop_100_strict$SS <- revalue(bg_all_three_AF_phylop_100_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_phylop_100_strict <- bg_all_three_AF_phylop_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_phylop_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
```

# all three 30
for comparison to AS-TC only events
## phastcons
try out randomly subsetting these lists multiple times and summarizing the results into one plot

```{r 30 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE[sample(1:length(all_three_AS_SE), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_all_three_SE_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_30$SS <- revalue(bg_all_three_SE_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_SE_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE_strict[sample(1:length(all_three_AS_SE_strict), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_all_three_SE_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_30_strict$SS <- revalue(bg_all_three_SE_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_all_three_SE_30_strict <-  bg_all_three_SE_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_all_three_SE_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 30 iterations for all three AF}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF[sample(1:length(all_three_AS_AF), 100, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 30}
bg_all_three_AF_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_100$SS <- revalue(bg_all_three_AF_100$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_AF_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
```

```{r 30 iterations for all three AF STRICT}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 30, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 30}
bg_all_three_AF_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_30_strict$SS <- revalue(bg_all_three_AF_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_30_strict <- bg_all_three_AF_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
```


## phyloP
```{r 30 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE[sample(1:length(all_three_AS_SE), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_all_three_SE_phylop_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_phylop_30$SS <- revalue(bg_all_three_SE_phylop_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_SE_phylop_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_SE <- all_three_AS_SE_strict[sample(1:length(all_three_AS_SE_strict), 30, replace=FALSE)]

test_all_three_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_all_three_SE_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_SE_phylop_30_strict$SS <- revalue(bg_all_three_SE_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_all_three_SE_phylop_30_strict <- bg_all_three_SE_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_all_three_SE_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 30 iterations for all three AF}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF[sample(1:length(all_three_AS_AF), 100, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 30}
bg_all_three_AF_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_phylop_100$SS <- revalue(bg_all_three_AF_phylop_100$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

ggplot(bg_all_three_AF_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
```

```{r 30 iterations for all three AF}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_all_three_AS_AF <- all_three_AS_AF_strict[sample(1:length(all_three_AS_AF_strict), 30, replace=FALSE)]

test_all_three_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_all_three_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_all_three_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_all_three_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r collapse all three AF 30}
bg_all_three_AF_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_all_three_AF_phylop_30_strict$SS <- revalue(bg_all_three_AF_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_all_three_AF_phylop_30_strict <- bg_all_three_AF_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_all_three_AF_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
```


# human chimp 100

## phastcons
```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE[sample(1:length(human_chimp_AS_SE), 100, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_SE_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_100$SS <- revalue(bg_human_chimp_SE_100$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_chimp_SE_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE_strict[sample(1:length(human_chimp_AS_SE_strict), 100, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_chimp_SE_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_100_strict$SS <- revalue(bg_human_chimp_SE_100_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_SE_100_strict <- bg_human_chimp_SE_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_chimp_SE_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 100 iterations for human chimp AF 100}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_AF_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for human chimp AF 100 strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF_strict[sample(1:length(human_chimp_AS_AF_strict), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_chimp_AF_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_AF_100_strict$SS <- revalue(bg_human_chimp_AF_100_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_AF_100_strict <- bg_human_chimp_AF_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250))


ggplot(bg_human_chimp_AF_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

## phyloP
```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE[sample(1:length(human_chimp_AS_SE), 100, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_SE_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_phylop_100$SS <- revalue(bg_human_chimp_SE_phylop_100$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_chimp_SE_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE_strict[sample(1:length(human_chimp_AS_SE_strict), 100, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_chimp_SE_phylop_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_phylop_100_strict$SS <- revalue(bg_human_chimp_SE_phylop_100_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_SE_phylop_100_strict <- bg_human_chimp_SE_phylop_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_chimp_SE_phylop_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


```{r 100 iterations for human chimp AF 100}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_AF_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for human chimp AF 100 strict }
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF_strict[sample(1:length(human_chimp_AS_AF_strict), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_chimp_AF_phylop_100_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_AF_phylop_100_strict$SS <- revalue(bg_human_chimp_AF_phylop_100_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_AF_phylop_100_strict <- bg_human_chimp_AF_phylop_100_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_human_chimp_AF_phylop_100_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


# human chimp 30

## phastcons
```{r 30 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE[sample(1:length(human_chimp_AS_SE), 30, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_human_chimp_SE_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_30$SS <- revalue(bg_human_chimp_SE_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_chimp_SE_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE_strict[sample(1:length(human_chimp_AS_SE_strict), 30, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_chimp_SE_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_30_strict$SS <- revalue(bg_human_chimp_SE_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_SE_30_strict <- bg_human_chimp_SE_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_chimp_SE_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 30 iterations for human chimp AF }
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 30, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_AF_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for human chimp AF strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF_strict[sample(1:length(human_chimp_AS_AF_strict), 30, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_chimp_AF_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_AF_30_strict$SS <- revalue(bg_human_chimp_AF_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_AF_30_strict <- bg_human_chimp_AF_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250))


ggplot(bg_human_chimp_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

## phyloP
```{r 30 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE[sample(1:length(human_chimp_AS_SE), 30, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_human_chimp_SE_phylop_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_phylop_30$SS <- revalue(bg_human_chimp_SE_phylop_30$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_chimp_SE_phylop_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE_strict[sample(1:length(human_chimp_AS_SE_strict), 30, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_chimp_SE_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_phylop_30_strict$SS <- revalue(bg_human_chimp_SE_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_SE_phylop_30_strict <- bg_human_chimp_SE_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_chimp_SE_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


```{r 100 iterations for human chimp AF 30}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 30, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations}
# maybe

bg_human_chimp_AF_phylop_30 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_phylop_30, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for human chimp AF 30 strict }
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF_strict[sample(1:length(human_chimp_AS_AF_strict), 30, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_chimp_AF_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_AF_phylop_30_strict$SS <- revalue(bg_human_chimp_AF_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_chimp_AF_phylop_30_strict <- bg_human_chimp_AF_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_human_chimp_AF_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

## human orang 100
## phastcons
```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_orang_AS_SE <- human_orang_AS_SE[sample(1:length(human_orang_AS_SE), 100, replace=FALSE)]

test_human_orang_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_orang_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_orang_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_orang_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_orang_SE_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_orang_SE_100$SS <- revalue(bg_human_orang_SE_100$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_orang_SE_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_orang_AS_SE <- human_orang_AS_SE_strict[sample(1:length(human_orang_AS_SE_strict), 30, replace=FALSE)]

test_human_orang_AS_SE_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_orang_AS_SE) %>% 
  mutate(type = "ctrl")

colnames(test_human_orang_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_orang_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_orang_SE_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_orang_SE_30_strict$SS <- revalue(bg_human_orang_SE_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_orang_SE_30_strict <- bg_human_orang_SE_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_orang_SE_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

```{r 30 iterations for human orang AF 30}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_AF_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 100 iterations for human orang AF 30 strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_orang_AS_AF <- human_orang_AS_AF_strict[sample(1:length(human_orang_AS_AF_strict), 30, replace=FALSE)]

test_human_orang_AS_AF_phastcons <- all_phastcons %>% 
  filter(event_id %in% test_human_orang_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_orang_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_orang_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_orang_AF_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_orang_AF_30_strict$SS <- revalue(bg_human_orang_AF_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_orang_AF_30_strict <- bg_human_orang_AF_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250))


ggplot(bg_human_orang_AF_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```

## phyloP
```{r 100 iterations for all three SE}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_SE <- human_chimp_AS_SE[sample(1:length(human_chimp_AS_SE), 100, replace=FALSE)]

test_human_chimp_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_chimp_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_SE_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_chimp_SE_phylop_100$SS <- revalue(bg_human_chimp_SE_phylop_100$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

ggplot(bg_human_chimp_SE_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for all three SE strict}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_orang_AS_SE <- human_orang_AS_SE_strict[sample(1:length(human_orang_AS_SE_strict), 30, replace=FALSE)]

test_human_orang_AS_SE_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_orang_AS_SE) %>% 
  mutate(type = "ctrl") 

colnames(test_human_orang_AS_SE_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_orang_AS_SE_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=case_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="Conservation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_SE)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 30 iterations strict}
# maybe

bg_human_orang_SE_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup() %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_orang_SE_phylop_30_strict$SS <- revalue(bg_human_orang_SE_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2", "4"="3"))
detach("package:plyr", unload=TRUE)

bg_human_orang_SE_phylop_30_strict <- bg_human_orang_SE_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-250,
                                  SS == 2 ~ x-50,
                                  SS == 3 ~ x-250)) 

ggplot(bg_human_orang_SE_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


```{r 100 iterations for human chimp AF 100}
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_chimp_AS_AF <- human_chimp_AS_AF[sample(1:length(human_chimp_AS_AF), 100, replace=FALSE)]

test_human_chimp_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_chimp_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_chimp_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_chimp_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations}
# maybe

bg_human_chimp_AF_phylop_100 <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y)) 

ggplot(bg_human_chimp_AF_phylop_100, aes(x=x, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(PANEL))
  
```

```{r 30 iterations for human orang AF strict }
plot_list <- list()

for (i in 1:100){
set.seed(99+i)
# seed 100 
test_human_orang_AS_AF <- human_orang_AS_AF_strict[sample(1:length(human_orang_AS_AF_strict), 30, replace=FALSE)]

test_human_orang_AS_AF_phastcons <- all_phylop %>% 
  filter(event_id %in% test_human_orang_AS_AF) %>% 
  mutate(type = "ctrl")

colnames(test_human_orang_AS_AF_phastcons)[10:309] <- c(1:300)

plot1 <- test_human_orang_AS_AF_phastcons %>% 
  gather(position, score, "1":"300") %>% 
  mutate(position = as.numeric(position)) %>% 
  group_by(event_id, type, SS) %>% 
  #mutate(position=caAF_when(SS == "0" ~ position -52,
  #                          SS == "1" ~ position -52,
  #                          TRUE ~ position -252)) %>% 
  ggplot(aes(x=position, y=score, group = type, color = type)) +
  geom_smooth(method = "gam", formula = y~s(x)) +
  scale_color_manual(values = c("grey"), name="") +
  labs(x="Position", y="ConAFrvation (Phastcons)") +
  facet_grid(cols = vars(SS), scales = "free_x", labeller = labeller(SS = labels_AF)) 
  #geom_vline(xintercept=0, color="grey")

  plot_list[[i]] <- ggplot_build(plot1)$data[[1]]
}

```

```{r extract data from plot and make average over 100 iterations strict}
# maybe

bg_human_orang_AF_phylop_30_strict <- do.call(rbind, plot_list) %>% 
  group_by(PANEL, x) %>% 
  mutate(m = mean(y), s = sd(y), e = std.error(y)) %>% 
  ungroup %>% 
  mutate(type = "ctrl", SS = PANEL)

library(plyr)
bg_human_orang_AF_phylop_30_strict$SS <- revalue(bg_human_orang_AF_phylop_30_strict$SS, c("1"="0", "2"="1", "3"="2"))
detach("package:plyr", unload=TRUE)

bg_human_orang_AF_phylop_30_strict <- bg_human_orang_AF_phylop_30_strict %>% 
  mutate(position_new = case_when(SS == 0 ~ (x-50),
                                  SS == 1 ~ x-50,
                                  SS == 2 ~ x-250)) 

ggplot(bg_human_orang_AF_phylop_30_strict, aes(x=position_new, y=m)) +
  geom_ribbon(aes(ymin = m-s, ymax= m+s), fill = "grey70") +
  geom_line(color = "black") +
  facet_grid(cols = vars(SS), scales = "free_x")
  
```


# save data
```{r save data}
save.image("~/Documents/05_results/01_primates/andrew_pipeline/remap_01_2020/conservation/remap_background_cons.RData")

```
